### 2012-05-22 inst/examples/policycosts/exact_npv.Rmd
cleanup

``` {r  bigloop}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````
Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,
``` {r  quadcosts}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.  
``` {r npv-plot}
npv0 <- dat[1,3] 
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

>>>>

``` {r  bigloop}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,

``` {r  quadcosts}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.

``` {r npv-plot}
npv0 <- dat[1,3] 
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

```{r }
dat <- data.table(dat)
dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]
````
